``Interestingness'' in Mathematical Theory Exploration

### 2019-10-18 PhDThesis/litreview_staticanalysis.tex
Add genetic patches

At the other end of the code improvement spectrum we find
\emph{superoptimisers}~\cite{massalin1987superoptimizer}, which can take an
arbitrarily long time to find improvements, but whose deductive power is only
limited by the undecidability of the source language. Superoptimisers, such as
\textsc{Souper}~\cite{sasnauskas2017souper} and \textsc{Aha!} (``A Hacker's
Assistant'', developed to accompany \emph{Hacker's
  Delight}~\cite{warren2013hacker}) treat the given code as a specification, and
perform an open-ended search through the space of all programs to find the
optimal implementation according to some quality measure or cost model.

>>>>

To find project-specific improvements we need some description or specification
of how our program \emph{should} behave, to judge proposed improvements against.
Few projects have a complete formal specification, due to the prohibitive cost
of creating, validating, verifying and maintaining such artefacts. Partial
specifications, in the form of automated test suites, are more common. These
have been used to automatically patch errors in code (i.e. altering code until
its test suite passes), using methods from evolutionary
computation~\cite{Forrest.Nguyen.Weimer.ea:2009,weimer2009automatically,Schulte.Forrest.Weimer:2010}.

Optimisations treat \empg{the code itself} as a specification: formally
describing the desired behaviour, but not prescribing the exact steps that
should be taken to implement it. This allows different implementations to be
used as long as the result is equivalent\footnote{Optimisation assumes that
  extra efficiency is always desirable. In some areas that is not the case, such
  as security-sensitive code, where speed ups may expose sensitive information
  to timings attacks~\cite{kocher1996timing}.}. Taking this to the extreme gives
rise to \emph{superoptimisation}~\cite{massalin1987superoptimizer}, which
performs an open-ended search through the space of all programs to find those
equivalent to the given code, which are also optimal according to some quality
measure or cost model. Superoptimisers, such a
s \textsc{Souper}~\cite{sasnauskas2017souper} and \textsc{Aha!} (``A Hacker's
Assistant'', developed to accompany \emph{Hacker's
  Delight}~\cite{warren2013hacker}), can take an arbitrarily long time to find
improvements, but their optimisation power is limited only by the undecidability
of the source language (optimisations which cannot be proven equivalent are
necessarily ignored, like the uncomputable improvements demonstrated by
Blum~\cite{blum1967machine}).
